---
title: "Exporting a chart"
description: >
  How to export a chart with DatawRappr
output:
  rmarkdown::html_vignette:
  toc: true
toc_depth: 2
number_sections: true
vignette: >
  %\VignetteIndexEntry{Exporting a chart}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(DatawRappr)
library(magick)
```

This article wants to provide a brief overview on How to export charts with `dw_export_chart()` via the Datawrapper-API.

## Arguments

In general there is a bunch of arguments that can be added to a call to Datawrapper's Export-API. You can check out the [documentation here](https://developer.datawrapper.de/docs/exporting-as-pdfsvg) or the [reference here](https://developer.datawrapper.de/reference#getchartsidexportformat). 

`dw_export_chart()` does not yet support all of these options. They are added step by step. Feel free to contribute the argument you're missing with [a pull request on Github](https://github.com/munichrocker/DatawRappr/pulls). 

For the moment, the most important arguments are supported (check the documentation `dw_export_chart()` for more):

* Changing the type of output: `type`
* Changing the unit of the output: `unit`
* The color mode: `mode`
* `width` and `height` in pixels
* Selection if titles should be included: set `plain` to `FALSE`
* The `scale` of the chart.
* A `border_width` argument, measured in pixels
* A argument to change the `border_color`
* Removing the background- and border-color by setting `transparent` to `TRUE`.

## PNG

Use the `type = "png"`-argument and download the result into an object. 

To save the image we are using {magick} which is a requirement for {DatawRappr}. Simply run `image_write()`:

```{r eval = FALSE}
png_chart <- dw_export_chart("CHART_ID", type = "png")

magick::image_write(png_chart, "OUTPUT.png")
```

## PDF

When loading a PDF with `type = "pdf"`, the data is transfered as a binary. Fir this you can use the builtin `writeBin`-function:

```{r eval = FALSE}
pdf_chart <- dw_export_chart("CHART_ID", type = "pdf")

writeBin(pdf_chart, con = "OUTPUT.pdf")
```

## SVG

When using `type = "svg"` you will retrieve the code for a svg. So saving is as simple as writing text to a file:

```{r eval = FALSE}
svg_chart <- dw_export_chart("CHART_ID", type = "svg")

fileConn <- file("OUTPUT.svg")
writeLines(svg_chart, fileConn)
close(fileConn)
```

