---
title: "Using the API"
description: >
  How to make simple API-calls
output: 
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 2
    number_sections: true
vignette: >
  %\VignetteIndexEntry{Using the API}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

# Making API-calls

## Create a chart

To **create an empty chart**, you can use

```{r}
dw_create_chart()
```

which will use the API key stored locally on your system. 

By default, Datawrapper will create an empty linechart, without a title. The function returns a **dw_chart**-object with the metadata-elements from the API. This object can be used to populate the `chart_id`-argument in all other functions - which means you don't have to deal with it. Just store the response from `dw_create_chart()` in your R-environment.

## Add data to the chart

To populate that chart with data, you can run

```{r}
dw_data_to_chart(
  x = DATAFRAME, 
  chart_id = CHART_ID_OR_dw_chart-object
  )
```

which uploads an R data.frame to an Datawrapper chart. 

The data.frame should already be in the right format, only including the expected columns for the chart. The API will asume, that the first row contains headers. If that's not true, you have to edit the metadata afterwards:

## Edit chart's metadata

```{r}
dw_edit_chart(
  chart_id = CHART_ID_OR_dw_chart-object, 
  title = "I'm a title", 
data = 
  list(
    `horizontal-header` = "false"
    )
)
```

Datawrapper offers a lot of variability in editing it's charts' metadata. You can find a whole [Documentation here](https://developer.datawrapper.de/docs/chart-properties-1).

To speed things up, the `dw_edit_chart()`-function has some built-in arguments for common transformations:

* `title`
* `intro` which is the text below the title
* `annotate` which is the text below the plot
* `byline` which is the name of the author
* `source_name` which states the source
* `source_url` which links to the source - but only if a `source_name` is provided

If you want to edit specific arguments in your plot, you can use the arguments `data`, `visualize`, `describe` and `publish` to include lists to the API call which change all possible settings in a chart, as shown in the example above.

When you're finished editing your chart, you might want to publish it:

```{r}
dw_publish_chart(
  chart_id = CHART_ID_OR_dw_chart-object
  )
```

This function returns a URL to the chart and the embed code, if you set the argument _return_urls_ to `TRUE`.

## Delete chart

Or you might want to delete a chart:

```{r}
dw_delete_chart(
  chart_id = CHART_ID_OR_dw_chart-object
  )
```

## Export chart

You can export charts as png - or even in pdf or svg, if you're using a paid plan.

```{r}
exported_chart <- dw_export_chart(
  chart_id = CHART_ID_OR_dw_chart-object, 
  type = c("png", "pdf", "svg")
  )
```

